Graph Generators: State of the Art and Open Challenges

### 2020-01-21 main.tex
Irena - grant no update

\begin{acks}
The authors would like to thank Dr. Kamesh Madduri for consultations and suggestions on the covered areas. The work of Sherif Sakr is funded by the European Regional Development Funds via the Mobilitas Plus programme (grant MOBTT75)
\end{acks}

>>>>

\begin{acks}
The authors would like to thank Dr. Kamesh Madduri for consultations and suggestions on the covered areas.
The work of Sherif Sakr is funded by the European Regional Development Funds via the Mobilitas Plus programme (grant MOBTT75).
The work of Irena Holubov\'{a} was partially funded by the GA\v{C}R project no. 19-01641S.
\end{acks}
